%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/mohamedsaqib/}{\Large Muhammad Saqib}} & Email : \href{mailto:saqib.arfeen@gmail.com}{saqib.arfeen@gmail.com}\\
\href{https://www.linkedin.com/in/mohamedsaqib/}{https://www.linkedin.com/in/mohamedsaqib/} & Mobile : +92 346 6311199 \\
  \href{https://github.com/saqibarfeen/}{https://github.com/saqibarfeen/}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National University of Computer and Emerging Sciences}{2012 -- 2016}
      {BS Computer Science, CGPA: 3.03/4.0}{}
 
  \resumeSubheading
  {Ayesha Bawany Govt. College}{2010 -- 2012}
  {Inter Pre-Engineering, 76\% marks}{}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
	
%	\resumeSubheading
%	{Panacloud}{}
%	{AI Bootcamp}{Sep 2017 - Present}
%	\resumeItemListStart
%	\item
%	{Learning state of the art technologies in data science and software development.}
%	\item
%	{Working and collaborating with fellow boot-campers in creating solutions ranging from GRPC server with browser client integration , to building ML models using Keras API.}
%	\resumeItemListEnd
	
	
	
    \resumeSubheading
      {Cloud9 Networks FZE}{UAE}
      {Sr. Software Engineer}{July 2016 - Present}
      \resumeItemListStart
        \resumeItem{Cloud Monitoring Software}
          {
          \begin{itemize}
          	\item {Research and solution design for Openstack private cloud infrastucture and services monitoring.}
          	\item {Development of the proposed design that included Sandboxed Lua plugins for Heka(github.com/mozilla/heka) and python plugins for collectd for data collection and processing and Elasticsearch , Logstash and Influxdb for Storage and retrieval and Kibana for Visualization.}
          	\item {Building grok and Lpeg patterns for various services of Openstack cloud: for parsing of machine data into fields for fast retrieval and visualization.}
          	\item {Security testing and best practices.}
          	\item {Built deployment puppet modules and manifests for 1-click deployment.}
  	\end{itemize}		
  		}
  	 \resumeItem{Network Monitoring System}
  	{
  		\begin{itemize}
  			\item {Competetor research and analysis of trends in the domain.}
  			\item {Implementing POC solutions with openssource tools and demonstrate them to decision makers.}
  			\item {Design ,development and intergration of existing opensource tools and in house built addons for network monitoing: incluuding querying of timeseries data from network devices and the storage , visualizatioona and reporting.}
  			\item {Elasticsearch , Logstash and Kibana for parsing, storage and retreival of syslog from devices ranging from PDUs to core switches.}
  			\item {Supporting deployment engineer and troubleshooting problems in deployment.}
  			
  		\end{itemize}
  	}
  \resumeItem{\href{https://github.com/pndaproject/}{PNDA Project}}
  {
  	\begin{itemize}
  	\item {Deployed PNDA Big data network analytics toolchain on Openstack cloud private.}
  	\item {Troubleshootiing of various SaltStack scripts and declarative states in the deployment process.}
  	\item {Providing support to various users of the opensource tool with problems specific to deployment on Openstack cloud.}
  \end{itemize}
}

\resumeItem{Big Data Analytics Engine}
{
	\begin{itemize}
	\item {Developing front-end forms and tables using server-side pagination with Angularjs framework 1.0.}
	\item {Writing REST api methods in Java Spring.}
	\item {Design and deployment of distributed hadoop backend- along with tools of the big-data ecosystem.}
	\item {Creating UI forms for establishing jdcp kafka connector for streaming data from Mysql and MsSQL databases;}
	\item {Aggregation and storage of data in HDFS.}
	\item {Created a solution for deduplication of records in HDFS byh scheduling Apache Oozie jobs.}
	
	
		
	\end{itemize}
}
 \resumeItem{KPK Govt. College Students Wifi Login Management System}
{
	\begin{itemize}
		\item {Analysis Design and implementation of the solution.}
		\item {Lead the development team.}
		\item {UI/UX process improvement and testing.}
		\item {Tracking code versions , branches and commits with git.}
	\end{itemize}
}
      \resumeItemListEnd

  

 %   \resumeSubheading
 %     {FAST-NU}{}
 %     {Research Assistant}{Jan 2015 - Dec 2015}
 %     \resumeItemListStart
 %       \resumeItem{Research Assistant - Machine Learning}
 %         {Research on machine learning for puzzle solving. Coded a prototype in python and trained it with tensorflow with GPU. http://dx.doi.org/10.14569/IJACSA.2017.080364 }
 %       \resumeItem{Teaching Assistant - Alogirithms \& Theory of Automata}
 %         {Helping students in their assignments and compilation of grade sheets. I had 150 students. }
 %     \resumeItemListEnd
  \resumeSubHeadingListEnd


%-------------------


%-----------SKILLS-----------------
\section{Skills}
\resumeSubHeadingListStart
\item
{Engineer robust systems with minimalist design and clean code.}
\item
{Hands-on expertise with cloud native technologies like Docker and Kubernetes and deployment of containerzed apps and Cloud IaaS namely AWS and Google Cloud.}
\item
{Experience with Big data and its tools like developing MapReduce in Java and working with Kafka, Zookeeper , Hive, Impala for reporting in HDFS.}
\item{
Expreience with Frontrend technologies : React 16 and Angular 1.0.
}
\item{
	Leading a team of entry-level engineers and training them.
}
\item{
Extensive experience with Python Django,Flask,OOP and Data science tools namely Pandas, Numpy, Keras and Tensorflow.
}
\item
{HPC distributed cluster system design and programming in MPI,Nvidia Cuda and OpenMP.}
\item{
Practical knowledge of HA and load balancers.}
\item{
Experience with relational,NoSql and time series databases namely MySql, MongoDB, Firebase , Influxdb, Graphite, Hive.
}
\item {
	{Proficient in Java, Python, JavaScript and C++.}
}
\resumeSubHeadingListEnd


%----------------------------------

%-----------PROJECTS-----------------
\section{Hobby Projects}
  \resumeSubHeadingListStart
      \resumeSubItem{Sokoban Solver}
  {Solving sokoban puzzle(an NP-Complete problem) with machine learning. Designed a recurrent neural network and generated data by SAT solver. \href {http://thesai.org/Downloads/Volume8No3/Paper_64-Generation_of_Sokoban_Stages_using_Recurrent.pdf}{White Paper}} 
	\resumeSubItem{Grpc api}
	{Grpc Nodejs api with Mongodb that out performs its json couterpart by 10-100x speed.}

    \resumeSubItem{Big data clusters}
      {Built virtual machine cluster for MPI and bare metal cluster system for hadoop mapreduce in HPC lab,FAST.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
